Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-13 paper/abstraction/paper.tex
add legend to figure 3

\sysname takes as input the network's abstract topology and its policy. The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous failures the network can withstand without losing connectivity.

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/example3}
  \vspace{-2.2em}
  \caption{An abstraction for the network in Figure~\ref{fig:example}.}
  \label{fig:example3}
  \vspace{-.8em}
\end{figure}

@@

Our topology abstractions can also capture concrete topologies; there will be a one-to-one correspondence between abstract and concrete nodes/edges. This allows operators to define complex networks in which some (e.g., legacy) parts of the network can not evolve while others can.
%It also means that our compiler subsumes those that operate only over concrete topologies.

@@

%
For each node in the abstract PG,
the idea is to infer facts learned about the number of disjoint paths
to groups of concrete routers in the node's role.
More specifically, we maintain fact of the form:
%
\[ \begin{array}{c}
  L_{X_1}, \ldots, L_{X_n}(j,k)
\end{array} \]
\noindent
%
where each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all". There is one label for each pod in the abstraction pod hierarchy under which the abstract node appears. For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the node itself.
Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for some/all pods $X_1, \ldots, X_{n-1}$
and for some/all groups of nodes in the role $X_n$ of size $j$,
%, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds. The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers,
there are $k$ paths to each such that all $j*k$ paths are edge-disjoint.

>>>>

\sysname takes as input the network's abstract topology and its policy. The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous link failures the network can withstand without losing connectivity.

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/example3}
  \vspace{-1.3em}
  \caption{An abstraction for the network in Figure~\ref{fig:example}.}
  \label{fig:example3}
  \vspace{-.6em}
\end{figure}

@@

Our topology abstractions can also capture concrete topologies by using a one-to-one correspondence between abstract and concrete nodes/edges. This allows operators to define complex networks in which some (e.g., legacy) parts of the network can not evolve while others can.
%It also means that our compiler subsumes those that operate only over concrete topologies.

@@

%
For each node in the abstract PG,
the idea is to infer facts learned about the number of edge-disjoint paths
to groups of concrete routers in the node's role.
More specifically, we maintain fact of the form:
%
\[ \begin{array}{c}
  L_{X_1}, \ldots, L_{X_n}(j,k)
\end{array} \]
\noindent
%
where each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all". There is one label for each pod in the abstraction pod hierarchy under which the abstract node appears. For a given node, $L_{X_1}$ corresponds to the outermost pod, $L_{X_{n-1}}$ corresponds to the innermost pod, and $L_{X_n}$ to the node itself.
Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete source node, for some/all pods $X_1, \ldots, X_{n-1}$
and for some/all groups of nodes in the role $X_n$ of size $j$,
%, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds. The base case $L_{X_n}(j,k)$ means that for "some"/``all" groups of size $j$ concrete routers,
there are $k$ paths to each such that all $j*k$ paths are edge-disjoint.
